A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-20 manuscript/manuscript.tex
touched up manuscript and arcana_paper class

We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)},
which enables the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
are implemented as Python classes, which define a range of potential derivatives and analysis methods.
Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
stores selected derivatives and associated provenance back into a repository for reuse by subsequent analyses.
Workflows are constructed using Nipype and can be executed on local workstations or in high performance
computing environments. Generic analysis methods can be consolidated within common
base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
requirements via class inheritance. Arcana therefore provides a platform to develop unified neuroimaging
workflows that can be reused across many research sites and studies.

@@

The utility of the Arcana framework is demonstrated by the
implementation of analysis suites for T1, T2* and diffusion weighted MRI
(dMRI) data and the application of dMRI tractogram \citep{tournier_mrtrix:_2012} and
composite vein image \citep{ward_combining_2018} workflows to data collected from a
healthy subject.

>>>>

We present a novel software framework, \emph{Abstraction of Repository-Centric ANAlysis (Arcana)},
which enables the development of complex, ``end-to-end'' workflows that are adaptable to new analyses and
portable to a wide range of computing infrastructures. Analysis templates for specific image types (e.g. MRI contrast)
are implemented as Python classes, which define a range of potential derivatives and analysis methods.
Arcana retrieves data from imaging repositories, which can be BIDS datasets, XNAT instances or plain directories, and
stores selected derivatives and associated provenance back into a repository for reuse by subsequent analyses.
Workflows are constructed using Nipype and can be executed on local workstations or in high performance
computing environments. Generic analysis methods can be consolidated within common
base classes to facilitate code-reuse and collaborative development, which can be specialised for study-specific
requirements via class inheritance. Arcana therefore provides a platform to develop unified and neuroimaging
workflows that can be reused across many research sites and studies.

@@

The utility of the Arcana framework is demonstrated by the
implementation of analysis suites for T1, T2* and diffusion weighted MRI
(dMRI) data and the application of dMRI tractogram \citep{tournier_mrtrix:_2012} and
vein masks \citep{ward_vein_2017} workflows to data collected from a
healthy subject.
